AA: the Algorithmic Auto-regulation (Software Development) Methodology

### 2013-05-31 front-matter.tex
acho que soh o titulo que mudei
minor fix in abstract

\title{
    AA: the Algoritmic Autoregulation Software Development Methodology
}

\author{%
Renato~Fabbri \and Ricardo~Fabbri \and Vilson Vieira \and Alexandre Negrao \and Lucas Zambianchi
\and Marcos Mendonca \and Danilo Shiga
}

@@

\begin{abstract}
We present a new methodology for coordinating
teamwork called Algorithmic Autoregulation (AA). This methodology is based on recent social networking concepts and individual merit and exhibits convenient asynchronous, autodocumenting and autoregulating characteristics. Team
members take on an egalitarian and volutary role, by logging into
periodic ``AA sessions'' for an arbitrary duration (e.g.\ 2 hours per day).
During each session, a user creates a log composed of short text sentences
about their activity. These logs are
publicly aggregated in a Website and are peer-validated, as in code
review. A short screencast is ideally recorded at the end of each session to make
AA logs more understandable. This methodology seems to be well-suited for
increasing the efficiency of teams working on
Global Software Development (GSD). Recognized reasons for this are
the: 1) builtin asynchronous
on-demand communication, documentation and working hours comprobatives;
2) reduced need for central management,
meetings and time-consuming reports. Hence, AA
legitimizes and eases activities of a distributed software team.  It
enables groups to have new means to fund activities,
allowing for business models to emerge from
distributed software development. AA is proposed,
at it's core, as a way of having self-replicating hacker initiatives. These claims are
discussed in a real case-study of a distributed free software
hacker team called Lab Macambira.
\end{abstract}

>>>>

\title{
    AA: the Algorithmic Auto-regulation (Software Development) Methodology
}

\author{%
Renato~Fabbri \and Ricardo~Fabbri \and Vilson Vieira \and Alexandre Negr\~{a}o \and Lucas Zambianchi
\and Marcos Mendonca \and Danilo Shiga
}

@@

\begin{abstract}
We present a new methodology for coordinating teamwork called Algorithmic
Auto-regulation (AA). This methodology is based on recent social networking
concepts and individual merit and exhibits convenient asynchronous,
auto-documenting and auto-regulating characteristics. Team members take on an
egalitarian and voluntary role, by logging into periodic ``AA sessions'' for an
arbitrary duration (e.g.\ 2 hours per day).  During each session, a user creates
a log composed of short text sentences about their activity. These logs are
publicly aggregated in a Website and are peer-validated, as in code review. A
short screen-cast is ideally recorded at the end of each session to make AA logs
more understandable. This methodology seems to be well-suited for increasing the
efficiency of teams working on Global Software Development (GSD). Recognized
reasons for this are the: 1) built-in asynchronous on-demand communication,
documentation and proven working hours; 2) reduced need for central management,
meetings and time-consuming reports. Hence, AA legitimizes and eases activities
of a distributed software team.  It enables groups to have new means to fund
activities, allowing for business models to emerge from distributed software
development. AA is proposed, at it's core, as a way of having self-replicating
hacker initiatives. These claims are discussed in a real case-study of a
distributed free software hacker team called Lab Macambira.
\end{abstract}
